Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-19 paper/main.tex
Minor equation fixes
updated main.tex with comments
added a few lines to the intro

\begin{itemize}
\item Benefits of combining human categorization information into ``topic models''
\item 
\end{itemize}

@@

\begin{equation}
\propto\prod_{i_{l,c}\in\mathcal{I}}\exp\left\{ -\frac{\left(\bar{z}^{T}\eta_{i_{l,c}}-a_{i_{l,c}}\right)^{2}}{2}\right\} p\left(a_{i_{l,c}}\mid\eta_{i_{l,c}}\right)\left(n_{d,\left(\cdot\right)}^{k,-\left(d,n\right)}+\alpha\beta_{k}\right)\frac{n_{\left(\cdot\right),w_{d,n}}^{k,-\left(d,n\right)}+\gamma}{\sum_{v=1}^{V}\left(n_{\left(\cdot\right),w_{d,n}}^{k,-\left(d,n\right)}+\gamma\right)}\label{eq:z-likelihood}\end{equation}

>>>>

There exist surprisingly many sources of unstructured text data that have been partially or completely categorized by human editors.  Examples include hierarchical directories of webpages \citep{DMOZ}, large hierarchically annotated product catalogs (e.g.~\citep{AMAZON} as available from \citep{SNAP}), manually annotated patient medical records, and many more.  In this work we show how to combine these two sources of information in a single model that allows us to, amongst other things, automatically annotate and/or categorize new text documents, effectively inserting them into the category

\begin{itemize}
\item Benefits of combining human categorization information into ``topic models''
\item LDA solved free text
\item supervised LDA improves LDA (extra info) and allows new inference (predict links, etc.)
\item amazon, freshdirect, netflix, dmoz, pandora (music genome)
\end{itemize}

@@

\begin{equation}
\propto\prod_{i_{l,c}\in\mathcal{I}}\exp\left\{ -\frac{\left(\bar{z}^{T}\eta_{i_{l,c}}-a_{i_{l,c}}\right)^{2}}{2}\right\} \left(n_{d,\left(\cdot\right)}^{k,-\left(d,n\right)}+\alpha\beta_{k}\right)\frac{n_{\left(\cdot\right),w_{d,n}}^{k,-\left(d,n\right)}+\gamma}{\sum_{v=1}^{V}\left(n_{\left(\cdot\right),w_{d,n}}^{k,-\left(d,n\right)}+\gamma\right)}\label{eq:z-likelihood}\end{equation}
